### 2019-02-26 sections/introduction.tex
some fixmes

\subsection{Task-oriented programming}
\fixme{Alejandro: Not entirely convincing}%Nico: hij heeft het hier volgens mij over de titel van de sectie en het woord aims in de eerste zin. Misschien moeten we een hardere claim doen hier?
% Task-Oriented Programming (\TOP) is a programming paradigm aimed at writing interactive multi-user applications in a declarative way \cite{conf/ppdp/PlasmeijerLMAK12}.
Task-oriented programming (\TOP) is a programming paradigm which aims to be the sweet spot between faithful modelling workflows
and rapid prototyping of multi-user web applications supporting these workflows.\fixme{Rinus: Hier zou ik een referentie naar ons ppdp2012 paper verwachten.}
% Task-oriented programming (\TOP) is a programming paradigm to support these ways of working.
\TOP focusses on modelling collaboration patterns.
This gives rise to user's need to interact and share information.
Next to that, \TOP automatically provides solutions to common development jobs like designing \GUI\ s, connecting to databases, and communicating between servers and clients.

>>>>

\subsection{Task-oriented programming}
\fixme{Alejandro: Not entirely convincing}%Nico: hij heeft het hier volgens mij over de titel van de sectie en het woord aims in de eerste zin. Misschien moeten we een hardere claim doen hier?
% Task-Oriented Programming (\TOP) is a programming paradigm aimed at writing interactive multi-user applications in a declarative way \cite{conf/ppdp/PlasmeijerLMAK12}.
Task-oriented programming (\TOP) is a programming paradigm which aims to be the sweet spot between faithful modelling workflows
and rapid prototyping of multi-user web applications supporting these workflows \cite{conf/ppdp/PlasmeijerLMAK12}.
% Task-oriented programming (\TOP) is a programming paradigm to support these ways of working.
\TOP focusses on modelling collaboration patterns.
This gives rise to user's need to interact and share information.
Next to that, \TOP automatically provides solutions to common development jobs like designing \GUI\ s, connecting to databases, and communicating between servers and clients.
